Automated iterative forecasting for the Portal Project

### 2018-02-02 manuscript/portal_iterative_forecasting_ms.Rmd
Make sure citations aren't treated as a link

Iterative forecasting requires data that is collected repeatedly, and it benefits most from data that is collected frequently, as this provides more opportunities for updating model results and assessing (and potentially improving) model performance [Box 1; @dietze2018]. The Portal Project is a long-term ecological study situated in the Chihuahuan Desert (2 km north and 6.5 km east of Portal, Arizona, US). Researchers have been continuously collecting data at the site since 1977, including data on the abundance of rodent and plant species (monthly and twice yearly, respectively) and climactic factors such as air temperature and precipitation (daily)[@brown1998; @ernest2009; @ernest2016]. The site consists of 24 50m x 50m experimental plots. Each plot contains 49 permanently marked trapping stations laid out in a 7 x 7 grid, and all plots are trapped with Sherman live traps for one night each month. For all rodents caught during a trapping session, information on species identity, size, and reproductive condition is collected, and new individuals are given identification tags. This data on rodent populations is high-frequency, uses consistent trapping methodology, and has an extended time-series (469 monthly samples and counting), making this study an ideal case for near-term iterative forecasting.

>>>>

Iterative forecasting requires data that is collected repeatedly, and it benefits most from data that is collected frequently, as this provides more opportunities for updating model results and assessing (and potentially improving) model performance [Box 1; @dietze2018]. The Portal Project is a long-term ecological study situated in the Chihuahuan Desert (2 km north and 6.5 km east of Portal, Arizona, US). Researchers have been continuously collecting data at the site since 1977, including data on the abundance of rodent and plant species (monthly and twice yearly, respectively) and climactic factors such as air temperature and precipitation (daily) [@brown1998; @ernest2009; @ernest2016]. The site consists of 24 50m x 50m experimental plots. Each plot contains 49 permanently marked trapping stations laid out in a 7 x 7 grid, and all plots are trapped with Sherman live traps for one night each month. For all rodents caught during a trapping session, information on species identity, size, and reproductive condition is collected, and new individuals are given identification tags. This data on rodent populations is high-frequency, uses consistent trapping methodology, and has an extended time-series (469 monthly samples and counting), making this study an ideal case for near-term iterative forecasting.
